More than one Author with different Affiliations

### 2016-04-15 NatPlant2/manuscript.tex
final submission

@@

@@

Because our modest sample size of fully sequenced individuals has limited power to infer recent population expansion, we investigated two alternative approaches for demographic inference.  
First, we utilized genotyping data from more than 4,000 maize landraces \cite{Hearne2015} to estimate the modern maize effective population size.
Because rare variants provide the best information about recent effective population sizes \cite{keinan2012}, we estimate $N_e$ using  a singleton-based estimator \cite{fu1993} of the population mutation rate $\theta=4N_e\mu$  and published values of the mutation rate \cite{clark2005} (see online methods for details). 
This yields a much higher estimate of the modern maize effective population size at  $N_m \approx 993,000$.
Finally, we employed a model-free coalescent approach \cite{schiffels2014} to estimate population size change using a subset of six genomes each of maize and teosinte.
Though this analysis suggests non-equilibrium dynamics for teosinte not included in our initial model, it is nonetheless broadly consistent with the other approaches, identifying population isolation beginning between 10,000 and 15,000 generations ago, a clear domestication bottleneck, and ultimately rapid population expansion in maize to an extremely large extant size of $\approx 10^9$ (Figure \ref{sFig:msmc}).
Our assessment of the historical demography of maize and teosinte provides context for subsequent analyses of linked selection.

@@

\subsection*{Hard sweeps do not explain diversity differences} %JRI
When selection increases the frequency of a new beneficial mutation, a signature of reduced diversity is left at surrounding linked sites \cite{smith1974}.
To evaluate whether patterns of such ``hard sweeps'' could explain observed differences in diversity between genic and intergenic regions of the genome, we compared diversity around missense and synonymous substitutions between \emph{Tripsacum} and either maize or teosinte.
If a substantial proportion of missense mutations have been fixed due to hard sweeps, diversity around these substitutions should be lower than around synonymous substitutions. 
We observe this pattern around the causative amino acid substitution in the maize domestication locus \emph{tga1} (Figure \ref{sFig:tga1}), likely the result of a hard sweep during domestication \cite{wang2015}. Genome-wide, however, we observe no differences in diversity at sites near synonymous versus missense substitutions in either maize or teosinte (Figure \ref{fig:hardSweeps}).

@@

Previous analyses have suggested that this approach may have limited power because a relatively high proportion of missense substitutions will be found in genes that, due to weak purifying selection, have higher genetic diversity \cite{enard2014}. 
To address this concern, we took advantage of genome-wide estimates of evolutionary constraint \cite{rodgers2015} calculated using genomic evolutionary rate profile (GERP) scores \cite{davydov2010}. 
We then evaluated substitutions only in subsets of genes in the highest and lowest 10\% quantile of mean GERP score, putatively representing genes under the strongest and weakest purifying selection. 
As expected, we see higher diversity around substitutions in genes under weak purifying selection, but we still find no difference in diversity near synonymous and missense substitutions in either subset of the data (Figure \ref{sFig:consUncons}).
Taken together, these data suggest hard sweeps do not play a major role in patterning genic diversity in either maize or teosinte.

@@

Our previous comparison of synonymous and missense substitutions has low power to detect the effects of selection acting on multiple beneficial mutations or standing genetic variation, because in such cases diversity around the substitution may be reduced to a lesser degree \cite{messer2013}. 
Nonetheless, such ``soft sweeps'' are still expected to occur more frequently in functional regions of the genome and could provide an alternative explanation to purifying selection for the observed reduction of diversity at linked sites in genes. 
To test this possibility, we performed a genome-wide scan for selection using the H12 statistic, a method expected to be sensitive to both hard and soft sweeps \cite{garud2015}. 
Qualitative differences between maize and teosinte in patterns of diversity within and outside of genes remained unchanged even after removing genes in the top 20\% quantile of H12 (Figure \ref{sFig:H12}A).
%\mbh{This makes me wonder about the top 20\%. Is the pattern of diversity reduction different in this fraction of the genome?  If so, that seems like something that should be mentioned.}
%TB Says: Sites in the top 20% of H12 are unlikely to be under background selection, so maize vs teo background selection pattern at these sites seems strange to investigate.
We interpret these combined results as suggesting that purifying selection has predominantly shaped diversity near genes and left a more pronounced signature in the teosinte genome due to the increased efficacy of selection resulting from differences in long-term effective population size.

@@

\subsection*{Population expansion leads to stronger purifying selection in modern maize} %JRI
Motivated by the rapid post-domestication expansion of maize evident in our demographic analyses, we reasoned that low-frequency --- and thus younger --- polymorphisms might show patterns distinct from pairwise diversity, which is determined primarily by intermediate frequency --- therefore comparably older --- alleles. 
Singleton diversity around missense and synonymous substitutions (Figure \ref{sFig:singleton}) appears nearly identical to results from pairwise diversity (Figure \ref{fig:hardSweeps}), providing little support for a substantial recent increase in the number or strength of hard sweeps occurring in maize.

In contrast, we observe a significant shift in the effects of purifying selection: singleton polymorphisms are more strongly reduced in and near genes in maize than in teosinte, even after downsampling our maize data to account for differences in sample size (Figure \ref{fig:purify}B). 
This result is the opposite of the pattern observed for $\pi$, where teosinte demonstrated a stronger reduction of diversity in and around genes than did maize. 
As before, this relationship remained after we removed the 20\% of genes with the highest H12 values (Figure \ref{sFig:H12}).
While direct comparison of pairwise and singleton diversity within taxa is consistent with non-equilibrium dynamics in teosinte, these too reveal much stronger differences in maize (Figure \ref{sFig:singletonPi}) and mirror results from simulations of purifying selection (Figure \ref{sFig:sims}).

@@

The absence of evidence for a genome-wide impact of hard sweeps in coding regions differs markedly from observations in \emph{Drosophila} \cite{sattath2011} and \emph{Capsella} \cite{williamson2014}, but is consistent with data from humans \cite{hernandez2011}.
Comparisons of the estimated percentages of nonsynonmyous substitutions fixed by natural selection \cite{ross2009,sella2009,eyre2009estimating,williamson2014} give similar results. 
While differences in long-term $N_e$ likely explains some of the observed variation across species, we see little change in the importance of hard sweeps in genes in singleton diversity in modern maize (Figure \ref{sFig:singleton}), perhaps suggesting other factors may contribute to these differences as well.  
One possibility, for example, is that, if mutational target size scales with genome size, the larger genomes of human and maize may offer more opportunities for noncoding loci to contribute to adaptation, with hard sweeps on nonsynonymous variants then playing a relatively smaller role. 
Support for this idea comes from numerous cases of adaptive transposable element insertion modifying gene regulation in maize \cite{studer2011,mao2015,yang2013} and studies of local adaptation that show enrichment for SNPs in regulatory regions in teosinte \cite{pyhajarvi2013} and humans \cite{fraser2013gene} but for nonsynonymous variants in the smaller \emph{Arabidopsis} genome \cite{hancock2011adaptation}.  
Our results, for example, are not dissimilar to findings in the comparably-sized mouse genome, where no differences are seen in diversity around nonsynonymous and synonymous substitutions in spite of a large $N_e$ and  as many as 80\% of adaptive substitutions occurring outside of genes\cite{Halligan:2013ir}.
Future comparative analyses using a common statistical framework (e.g. \cite{corbett2015} )and considering additional ecological and life history factors (c.f. \cite{leffler2012}) should allow explicit testing of this idea.

\subsection*{Demography influences the efficiency of purifying selection} 
One of our more striking findings is that the impact of purifying selection on maize and teosinte qualitatively changed over time. 
We observe a more pronounced decrease in $\pi$ around genes in teosinte than maize (Figure \ref{fig:purify}A), but the opposite trend when we evaluate diversity using singleton polymorphisms (Figure \ref{fig:purify}B).
The efficiency of purifying selection is proportional to effective population size \cite{kimura1984}, and these results are thus consistent with our demographic analyses which show a domestication bottleneck and smaller long-term $N_e$ in maize \cite{eyre1998, tenaillon2004, wright2005, ross2009} followed by recent rapid expansion and a much larger modern $N_e$. 
Simple foward-in-time population genetic simulations qualitatively confirm these results, and further suggest that the observed patterns are likely cause by sites under relatively weak purifying selection \ref{sFig:sims}.

@@

\subsection*{Plant materials}
We made use of published sequences from inbred accessions of teosinte (Z. {\it mays} ssp. {\it parviglumis}) and maize landraces from the Maize HapMap3 panel as part of the Panzea project  \cite{chia2012, lemmon2014, bukowski2015}. 
From these data, we removed 4 teosinte individuals that were not ssp. \textit{parviglumis} or appeared as outliers in an initial principal component analysis conducted with the package adegenet \cite{jombart2011} (Figure \ref{sFig:PCA}), leaving 13 teosinte and 23 maize that were used for all subsequent analyses (Table \ref{sTab:list}). We also utilized a single individual of (\textit{Tripsacum dactyloides}) as an outgroup.  All bam files are available at \url{/iplant/home/shared/panzea/hapmap3/bam\_internal/v3\_bams\_bwamem}.

@@

\subsection*{Demographic inference}
We used the software $\delta$a$\delta$i \cite{gutenkunst2009} to estimate parameters of a domestication bottleneck from the joint maize-teosinte SFS, using only sites $>5 kb$ from a gene to ameliorate the effects of linked selection.
To minimize the number of parameters estimated, we employed a simple demographic model which posits a teosinte population of constant effective size $N_a$.  At time $T_b$ generations in the past, this population gave rise to a maize population of size $N_b$ which grew exponentially to size $N_m$ in the present (Figure \ref{fig:bottleneck}).
The model includes migration of $M_{mt}$ individuals each generation from maize to teosinte and $M_{tm}$ individuals from teosinte to maize.  We estimated $N_a$ using $\delta$a$\delta$i's estimation of $\theta=4N_a\mu$ from the data and a mutation rate of $\mu = 3 \times 10^{-8}$ \cite{clark2005}. 
We estimated all other parameters using 1,000 $\delta$a$\delta$i optimizations and allowing initial values between runs to be randomly perturbed by a factor of 2.  
Optimized parameters along with their initial values and upper and lower bounds can be found in table \ref{sTab:dadi}. We report parameter estimates from the optimization run with the highest log-likelihood.

@@

As a final estimate of demography, we employed MSMC \cite{schiffels2014}  to complement our model-based demographic inference. 
We used six each of maize and teosinte (BKN022, BKN025, BKN029, BKN030, BKN031, BKN033, TIL01, TIL03, TIL09, TIL10, TIL11 and TIL14), treating each inbred genome as a single haplotype.
We called SNPs in ANGSD \cite{korneliussen2014} using a SNP p-value of $1e-6$ against a reference genome masked using SNPable (\url{http://lh3lh3.users.sourceforge.net/snpable.shtml}). 
We then removed heterozygous genotypes and filtered sites with a mapping quality $<30$, a base quality $<20$, or a $|\textit{log}_2(\text{depth})|<1$.
We ran MSMC with pattern parameter $20\times2+20\times4+10\times2$ (Figure \ref{sFig:msmc}A) for population size inference. To estimate the rate of cross-coalescence we used four maize and four teosinte haplotypes with pattern parameter $20\times1 + 20\times2$ (Figure \ref{sFig:msmc}B).

@@

@@

{\scriptsize \sf
\renewcommand{\baselinestretch}{2.0}
\bibliographystyle{naturemag}
\bibliography{Reference}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% Supporting info below this line %%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\onecolumn
\section*{Supporting Information}
\renewcommand\thefigure{S\arabic{figure}}
\renewcommand\thetable{S\arabic{table}}    
\setcounter{figure}{0}
\setcounter{table}{0}

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=\textwidth]{FigsAndFiles/plotDiversity_TvM_Folded2_Significance_tga1Supp_June.png}
    \end{center}
\caption{Diversity surrounding the causative substitution at the \emph{tga1} locus.  \label{sFig:tga1}}
\end{figure}
\clearpage

\begin{figure}
  \includegraphics[width=.5\textwidth]{FigsAndFiles/TIL_BKN_bootstrapping_msmc2_labeled.pdf}
  \includegraphics[width=.5\textwidth]{FigsAndFiles/relativeCrossCoalescenceRate_labeled.pdf}
\caption{MSMC Analyses. Shown in \textbf{A} are effective population size estimates over time. Estimates are depicted as solid lines and boostrap resampling is represented with dotted lines for both maize (red) and teosinte (blue). \textbf{B} depticts the relative cross-coalescence rate between maize and teosinte estimated using MSMC. In both panels, time is estimated assuming an annual generation time and a mutation rate of $\mu=3\times 10^{-8}$ \label{sFig:msmc}}
\end{figure}
\clearpage

\begin{figure}
  \includegraphics[width=.5\textwidth]{FigsAndFiles/plotDiversity_TvM_Conserved_Significance_June.png}
  \includegraphics[width=.5\textwidth]{FigsAndFiles/plotDiversity_TvM_Unconserved_Significance_June.png}
\caption{ Pairwise diversity surrounding synonymous and nonsynonymous
  substitutions in maize at \textbf{A} highly conserved or \textbf{B}  unconserved sites.  Bootstrap-based 95\% confidence intervals are depicted via shading. Inset plots depict a larger range on the x-axis. \label{sFig:consUncons}}
\end{figure}
\clearpage

\begin{figure}
  \includegraphics[width=\textwidth]{FigsAndFiles/plotDiversity_TvM_Singletons.png}
\caption{ Singleton diversity surrounding synonymous and nonsynonymous
  substitutions in maize. \label{sFig:singleton}}
\end{figure}
\clearpage

\begin{figure}
  \includegraphics[width=\textwidth]{FigsAndFiles/distanceToGene_WithSignificance_Folded2_maizeAndTeoSingleVsPi.png}
\caption{ Relative diversity versus distance to nearest gene in maize and teosinte. Relative diversity is calculated by comparing to the mean diversity in all windows $\geq 0.02 cM$ from the nearest gene. Lines depict cubic smoothing splines with smoothing parameters chosen via generalized cross validation and shading depicts bootstrap-based 95\% confidence intervals.  \label{sFig:singletonPi}}
\end{figure}
\clearpage

\begin{figure}
  \includegraphics[width=\textwidth]{FigsAndFiles/jri_sims.png}
\caption{Simulations of diversity statistics in maize and teosinte with varying strengths of purifying selection. Points show the mean ($\pm$ standard error) of the population mutation rate $\theta$ estimated by singletons ($\eta_1$) and pairwise differences ($\pi$). \label{sFig:sims}}
\end{figure}
\clearpage

\begin{figure}
  \includegraphics[width=.5\textwidth]{FigsAndFiles/distanceToGene_Unselected_manuscript.png}
    \includegraphics[width=.5\textwidth]{FigsAndFiles/distanceToGene_unselected_Singletons_manuscript.png}
\caption{ Relative level of diversity versus distance to the nearest gene, in maize and teosinte, based on only sites that do not show evidence of hard or soft sweeps according to H12. Two measures of diversity were investigated. {\bf A} displays pairwise diversity,
which is most influenced by intermediate frequency alleles and therefore depicts more ancient evolutionary patterns, and {\bf B} depicts singleton diversity, influenced by rare alleles and thus depicting evolutionary patterns in the recent past. Bootstrap-based 95\% confidence intervals are depicted via shading. Inset plots depict a smaller range on the x-axis. \label{sFig:H12}}
\end{figure}
\clearpage

\begin{figure}
  \begin{center}
  \includegraphics[width=.75\textwidth]{FigsAndFiles/tilPCA_aug.pdf}\\
  \includegraphics[width=.75\textwidth]{FigsAndFiles/bknPCA_aug.pdf}\\
  \end{center}
  \caption{Principal component analysis of teosinte and maize individuals to ensure that no close relatives were inadvertantly included in our study. Plots are based on a random sample of 10,000 SNPs. {\bf A} displays the percentage of total variance explained by each principal component for teosinte, while {\bf B} shows PC1 vs PC2 for all 13 teosinte individuals. Simlarly, {\bf C} depicts the percentage of total variance explained by each principal component for maize, and {\bf D} shows PC1 vs PC2 for all 23 maize individuals. \label{sFig:PCA}}
\end{figure}
\clearpage

\begin{table}[h]  
  \begin{center}
  \begin{tabular}{c|c}
    \bf Maize & \bf Teosinte \\ \hline \hline
    BKN009 &  TIL01 \\
    BKN010 & TIL02 \\
    BKN011 & TIL03 \\
    BKN014 & TIL04-TIP454 \\
    BKN015 & TIL07 \\
    BKN016 & TIL09 \\
    BKN017 & TIL10 \\
    BKN018 & TIL11 \\
    BKN019 & TIL12 \\
    BKN020 & TIL14-TIP498 \\
    BKN022 & TIL15 \\
    BKN023 & TIL16 \\
    BKN025 & TIL17 \\
    BKN026 & \\
    BKN027 & \\
    BKN029 & \\
    BKN030 & \\
    BKN031 & \\
    BKN032 & \\
    BKN033 & \\
    BKN034 & \\
    BKN035 & \\
    BKN040 & \\ \hline
  \end{tabular}
  \end{center}
  \caption{A list of maize and teosinte individuals included in this study. Sequencing and details were previously described by \cite{chia2012}   } \label{sTab:list}
\end{table}
\clearpage

>>>>

%\renewcommand{\abstractname}{\vspace{-\baselineskip}}
\renewcommand{\abstractname}{Abstract (opening paragraph)}

@@

\newcounter{firstbib} % bibliography counter

@@

Because our modest sample size of fully sequenced individuals has limited power to infer recent population expansion, we investigated two alternative approaches for demographic inference.  
First, we utilized genotyping data from more than 4,000 maize landraces \cite{Hearne2015} to estimate the modern maize effective population size.
Because rare variants provide the best information about recent effective population sizes \cite{keinan2012}, we estimate $N_e$ using  a singleton-based estimator \cite{fu1993} of the population mutation rate $\theta=4N_e\mu$  and published values of the mutation rate \cite{clark2005} (see online methods for details). 
This yields a much higher estimate of the modern maize effective population size at  $N_m \approx 993,000$.
Finally, we employed a model-free coalescent approach \cite{schiffels2014} to estimate population size change using a subset of six genomes each of maize and teosinte.
Though this analysis suggests non-equilibrium dynamics for teosinte not included in our initial model, it is nonetheless broadly consistent with the other approaches, identifying population isolation beginning between 10,000 and 15,000 generations ago, a clear domestication bottleneck, and ultimately rapid population expansion in maize to an extremely large extant size of $\approx 10^9$ (Figure S2).
Our assessment of the historical demography of maize and teosinte provides context for subsequent analyses of linked selection.

@@

\subsection*{Hard sweeps do not explain diversity differences} %JRI
When selection increases the frequency of a new beneficial mutation, a signature of reduced diversity is left at surrounding linked sites \cite{smith1974}.
To evaluate whether patterns of such ``hard sweeps'' could explain observed differences in diversity between genic and intergenic regions of the genome, we compared diversity around missense and synonymous substitutions between \emph{Tripsacum} and either maize or teosinte.
If a substantial proportion of missense mutations have been fixed due to hard sweeps, diversity around these substitutions should be lower than around synonymous substitutions. 
We observe this pattern around the causative amino acid substitution in the maize domestication locus \emph{tga1} (Figure S1), likely the result of a hard sweep during domestication \cite{wang2015}. Genome-wide, however, we observe no differences in diversity at sites near synonymous versus missense substitutions in either maize or teosinte (Figure \ref{fig:hardSweeps}).

@@

Previous analyses have suggested that this approach may have limited power because a relatively high proportion of missense substitutions will be found in genes that, due to weak purifying selection, have higher genetic diversity \cite{enard2014}. 
To address this concern, we took advantage of genome-wide estimates of evolutionary constraint \cite{rodgers2015} calculated using genomic evolutionary rate profile (GERP) scores \cite{davydov2010}. 
We then evaluated substitutions only in subsets of genes in the highest and lowest 10\% quantile of mean GERP score, putatively representing genes under the strongest and weakest purifying selection. 
As expected, we see higher diversity around substitutions in genes under weak purifying selection, but we still find no difference in diversity near synonymous and missense substitutions in either subset of the data (Figure S3).
Taken together, these data suggest hard sweeps do not play a major role in patterning genic diversity in either maize or teosinte.

@@

Our previous comparison of synonymous and missense substitutions has low power to detect the effects of selection acting on multiple beneficial mutations or standing genetic variation, because in such cases diversity around the substitution may be reduced to a lesser degree \cite{messer2013}. 
Nonetheless, such ``soft sweeps'' are still expected to occur more frequently in functional regions of the genome and could provide an alternative explanation to purifying selection for the observed reduction of diversity at linked sites in genes. 
To test this possibility, we performed a genome-wide scan for selection using the H12 statistic, a method expected to be sensitive to both hard and soft sweeps \cite{garud2015}. 
Qualitative differences between maize and teosinte in patterns of diversity within and outside of genes remained unchanged even after removing genes in the top 20\% quantile of H12 (Figure S7A).
%\mbh{This makes me wonder about the top 20\%. Is the pattern of diversity reduction different in this fraction of the genome?  If so, that seems like something that should be mentioned.}
%TB Says: Sites in the top 20% of H12 are unlikely to be under background selection, so maize vs teo background selection pattern at these sites seems strange to investigate.
We interpret these combined results as suggesting that purifying selection has predominantly shaped diversity near genes and left a more pronounced signature in the teosinte genome due to the increased efficacy of selection resulting from differences in long-term effective population size.

@@

\subsection*{Population expansion leads to stronger purifying selection in modern maize} %JRI
Motivated by the rapid post-domestication expansion of maize evident in our demographic analyses, we reasoned that low-frequency --- and thus younger --- polymorphisms might show patterns distinct from pairwise diversity, which is determined primarily by intermediate frequency --- therefore comparably older --- alleles. 
Singleton diversity around missense and synonymous substitutions (Figure S4) appears nearly identical to results from pairwise diversity (Figure \ref{fig:hardSweeps}), providing little support for a substantial recent increase in the number or strength of hard sweeps occurring in maize.

In contrast, we observe a significant shift in the effects of purifying selection: singleton polymorphisms are more strongly reduced in and near genes in maize than in teosinte, even after downsampling our maize data to account for differences in sample size (Figure \ref{fig:purify}B). 
This result is the opposite of the pattern observed for $\pi$, where teosinte demonstrated a stronger reduction of diversity in and around genes than did maize. 
As before, this relationship remained after we removed the 20\% of genes with the highest H12 values (Figure S7).
While direct comparison of pairwise and singleton diversity within taxa is consistent with non-equilibrium dynamics in teosinte, these too reveal much stronger differences in maize (Figure S5) and mirror results from simulations of purifying selection (Figure S6).

@@

The absence of evidence for a genome-wide impact of hard sweeps in coding regions differs markedly from observations in \emph{Drosophila} \cite{sattath2011} and \emph{Capsella} \cite{williamson2014}, but is consistent with data from humans \cite{hernandez2011}.
Comparisons of the estimated percentages of nonsynonmyous substitutions fixed by natural selection \cite{ross2009,sella2009,eyre2009estimating,williamson2014} give similar results. 
While differences in long-term $N_e$ likely explains some of the observed variation across species, we see little change in the importance of hard sweeps in genes in singleton diversity in modern maize (Figure S4), perhaps suggesting other factors may contribute to these differences as well.  
One possibility, for example, is that, if mutational target size scales with genome size, the larger genomes of human and maize may offer more opportunities for noncoding loci to contribute to adaptation, with hard sweeps on nonsynonymous variants then playing a relatively smaller role. 
Support for this idea comes from numerous cases of adaptive transposable element insertion modifying gene regulation in maize \cite{studer2011,mao2015,yang2013} and studies of local adaptation that show enrichment for SNPs in regulatory regions in teosinte \cite{pyhajarvi2013} and humans \cite{fraser2013gene} but for nonsynonymous variants in the smaller \emph{Arabidopsis} genome \cite{hancock2011adaptation}.  
Our results, for example, are not dissimilar to findings in the comparably-sized mouse genome, where no differences are seen in diversity around nonsynonymous and synonymous substitutions in spite of a large $N_e$ and  as many as 80\% of adaptive substitutions occurring outside of genes\cite{Halligan:2013ir}.
Future comparative analyses using a common statistical framework (e.g. \cite{corbett2015} )and considering additional ecological and life history factors (c.f. \cite{leffler2012}) should allow explicit testing of this idea.

\subsection*{Demography influences the efficiency of purifying selection} 
One of our more striking findings is that the impact of purifying selection on maize and teosinte qualitatively changed over time. 
We observe a more pronounced decrease in $\pi$ around genes in teosinte than maize (Figure \ref{fig:purify}A), but the opposite trend when we evaluate diversity using singleton polymorphisms (Figure \ref{fig:purify}B).
The efficiency of purifying selection is proportional to effective population size \cite{kimura1984}, and these results are thus consistent with our demographic analyses which show a domestication bottleneck and smaller long-term $N_e$ in maize \cite{eyre1998, tenaillon2004, wright2005, ross2009} followed by recent rapid expansion and a much larger modern $N_e$. 
Simple foward-in-time population genetic simulations qualitatively confirm these results, and further suggest that the observed patterns are likely cause by sites under relatively weak purifying selection (Figure S6).

@@

\subsection*{Plant materials}
We made use of published sequences from inbred accessions of teosinte (Z. {\it mays} ssp. {\it parviglumis}) and maize landraces from the Maize HapMap3 panel as part of the Panzea project  \cite{chia2012, lemmon2014, bukowski2015}. 
From these data, we removed 4 teosinte individuals that were not ssp. \textit{parviglumis} or appeared as outliers in an initial principal component analysis conducted with the package adegenet \cite{jombart2011} (Figure S8), leaving 13 teosinte and 23 maize that were used for all subsequent analyses (Table S1). We also utilized a single individual of (\textit{Tripsacum dactyloides}) as an outgroup.  All bam files are available from Cyverse at \url{/iplant/home/shared/data_commons/curated/Beissinger_MaizeTeo_2016}.

@@

\subsection*{Demographic inference}
We used the software $\delta$a$\delta$i \cite{gutenkunst2009} to estimate parameters of a domestication bottleneck from the joint maize-teosinte SFS, using only sites $>5 kb$ from a gene to ameliorate the effects of linked selection.
To minimize the number of parameters estimated, we employed a simple demographic model which posits a teosinte population of constant effective size $N_a$.  At time $T_b$ generations in the past, this population gave rise to a maize population of size $N_b$ which grew exponentially to size $N_m$ in the present (Figure \ref{fig:bottleneck}).
The model includes migration of $M_{mt}$ individuals each generation from maize to teosinte and $M_{tm}$ individuals from teosinte to maize.  We estimated $N_a$ using $\delta$a$\delta$i's estimation of $\theta=4N_a\mu$ from the data and a mutation rate of $\mu = 3 \times 10^{-8}$ \cite{clark2005}. 
We estimated all other parameters using 1,000 $\delta$a$\delta$i optimizations and allowing initial values between runs to be randomly perturbed by a factor of 2.  
Optimized parameters along with their initial values and upper and lower bounds can be found in table S2. We report parameter estimates from the optimization run with the highest log-likelihood.

@@

As a final estimate of demography, we employed MSMC \cite{schiffels2014}  to complement our model-based demographic inference. 
We used six each of maize and teosinte (BKN022, BKN025, BKN029, BKN030, BKN031, BKN033, TIL01, TIL03, TIL09, TIL10, TIL11 and TIL14), treating each inbred genome as a single haplotype.
We called SNPs in ANGSD \cite{korneliussen2014} using a SNP p-value of $1e-6$ against a reference genome masked using SNPable (\url{http://lh3lh3.users.sourceforge.net/snpable.shtml}). 
We then removed heterozygous genotypes and filtered sites with a mapping quality $<30$, a base quality $<20$, or a $|\textit{log}_2(\text{depth})|<1$.
We ran MSMC with pattern parameter $20\times2+20\times4+10\times2$ (Figure S2A) for population size inference. To estimate the rate of cross-coalescence we used four maize and four teosinte haplotypes with pattern parameter $20\times1 + 20\times2$ (Figure \S2B).

@@

\section*{Correspondence}
Correspondence may be addressed to Tim Beissinger (beissingert@missouri.edu) or Jeffrey Ross-Ibarra (rossibarra@ucdavis.edu)

@@

%{\scriptsize \sf
%\renewcommand{\baselinestretch}{2.0}
%\bibliographystyle{naturemag}
%\bibliography{Reference}
%}

\renewcommand\refname{References (Main Text)}

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem{dobzhansky1957}
\bibinfo{author}{Dobzhansky, T.} \& \bibinfo{author}{Pavlovsky, O.}
\newblock \bibinfo{title}{An experimental study of interaction between genetic
  drift and natural selection}.
\newblock \emph{\bibinfo{journal}{Evolution}} \bibinfo{pages}{311--319}
  (\bibinfo{year}{1957}).

\bibitem{voight2005}
\bibinfo{author}{Voight, B.~F.} \emph{et~al.}
\newblock \bibinfo{title}{Interrogating multiple aspects of variation in a full
  resequencing data set to infer human population size changes}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences of the United States of America}} \textbf{\bibinfo{volume}{102}},
  \bibinfo{pages}{18508--18513} (\bibinfo{year}{2005}).

\bibitem{gutenkunst2009}
\bibinfo{author}{Gutenkunst, R.~N.}, \bibinfo{author}{Hernandez, R.~D.},
  \bibinfo{author}{Williamson, S.~H.} \& \bibinfo{author}{Bustamante, C.~D.}
\newblock \bibinfo{title}{Inferring the joint demographic history of multiple
  populations from multidimensional snp frequency data}.
\newblock \emph{\bibinfo{journal}{PLoS genetics}} \textbf{\bibinfo{volume}{5}},
  \bibinfo{pages}{e1000695} (\bibinfo{year}{2009}).

\bibitem{akey2009}
\bibinfo{author}{Akey, J.~M.}
\newblock \bibinfo{title}{Constructing genomic maps of positive selection in
  humans: Where do we go from here?}
\newblock \emph{\bibinfo{journal}{Genome research}}
  \textbf{\bibinfo{volume}{19}}, \bibinfo{pages}{711--722}
  (\bibinfo{year}{2009}).

\bibitem{smith1974}
\bibinfo{author}{Smith, J.~M.} \& \bibinfo{author}{Haigh, J.}
\newblock \bibinfo{title}{The hitch-hiking effect of a favourable gene}.
\newblock \emph{\bibinfo{journal}{Genetical research}}
  \textbf{\bibinfo{volume}{23}}, \bibinfo{pages}{23--35}
  (\bibinfo{year}{1974}).

\bibitem{slotte2014}
\bibinfo{author}{Slotte, T.}
\newblock \bibinfo{title}{The impact of linked selection on plant genomic
  variation}.
\newblock \emph{\bibinfo{journal}{Briefings in functional genomics}}
  \textbf{\bibinfo{volume}{13}}, \bibinfo{pages}{268--275}
  (\bibinfo{year}{2014}).

\bibitem{charlesworth1993}
\bibinfo{author}{Charlesworth, B.}, \bibinfo{author}{Morgan, M.} \&
  \bibinfo{author}{Charlesworth, D.}
\newblock \bibinfo{title}{The effect of deleterious mutations on neutral
  molecular variation.}
\newblock \emph{\bibinfo{journal}{Genetics}} \textbf{\bibinfo{volume}{134}},
  \bibinfo{pages}{1289--1303} (\bibinfo{year}{1993}).

\bibitem{sella2009}
\bibinfo{author}{Sella, G.}, \bibinfo{author}{Petrov, D.~A.},
  \bibinfo{author}{Przeworski, M.} \& \bibinfo{author}{Andolfatto, P.}
\newblock \bibinfo{title}{Pervasive natural selection in the drosophila
  genome?}
\newblock \emph{\bibinfo{journal}{PLoS genetics}} \textbf{\bibinfo{volume}{5}},
  \bibinfo{pages}{e1000495} (\bibinfo{year}{2009}).

\bibitem{elyashiv2014}
\bibinfo{author}{Elyashiv, E.} \emph{et~al.}
\newblock \bibinfo{title}{A genomic map of the effects of linked selection in
  drosophila}.
\newblock \emph{\bibinfo{journal}{arXiv preprint arXiv:1408.5461}}
  (\bibinfo{year}{2014}).

\bibitem{andolfatto2005}
\bibinfo{author}{Andolfatto, P.}
\newblock \bibinfo{title}{Adaptive evolution of non-coding dna in drosophila}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{437}},
  \bibinfo{pages}{1149--1152} (\bibinfo{year}{2005}).

\bibitem{cutter2013}
\bibinfo{author}{Cutter, A.~D.} \& \bibinfo{author}{Payseur, B.~A.}
\newblock \bibinfo{title}{Genomic signatures of selection at linked sites:
  unifying the disparity among species}.
\newblock \emph{\bibinfo{journal}{Nature Reviews Genetics}}
  \textbf{\bibinfo{volume}{14}}, \bibinfo{pages}{262--274}
  (\bibinfo{year}{2013}).

\bibitem{corbett2015}
\bibinfo{author}{Corbett-Detig, R.~B.}, \bibinfo{author}{Hartl, D.~L.} \&
  \bibinfo{author}{Sackton, T.~B.}
\newblock \bibinfo{title}{Natural selection constrains neutral diversity across
  a wide range of species}.
\newblock \emph{\bibinfo{journal}{PLoS Biol}} \textbf{\bibinfo{volume}{13}},
  \bibinfo{pages}{e1002112} (\bibinfo{year}{2015}).
\newblock \urlprefix\url{http://dx.doi.org/10.1371%2Fjournal.pbio.1002112}.

\bibitem{leffler2012}
\bibinfo{author}{Leffler, E.~M.} \emph{et~al.}
\newblock \bibinfo{title}{Revisiting an old riddle: what determines genetic
  diversity levels within species}.
\newblock \emph{\bibinfo{journal}{PLoS Biol}} \textbf{\bibinfo{volume}{10}},
  \bibinfo{pages}{e1001388} (\bibinfo{year}{2012}).

\bibitem{duchen2013}
\bibinfo{author}{Duchen, P.}, \bibinfo{author}{{\v{Z}}ivkovi{\'c}, D.},
  \bibinfo{author}{Hutter, S.}, \bibinfo{author}{Stephan, W.} \&
  \bibinfo{author}{Laurent, S.}
\newblock \bibinfo{title}{Demographic inference reveals african and european
  admixture in the north american drosophila melanogaster population}.
\newblock \emph{\bibinfo{journal}{Genetics}} \textbf{\bibinfo{volume}{193}},
  \bibinfo{pages}{291--301} (\bibinfo{year}{2013}).

\bibitem{reich1998}
\bibinfo{author}{Reich, D.~E.} \& \bibinfo{author}{Goldstein, D.~B.}
\newblock \bibinfo{title}{Genetic evidence for a paleolithic human population
  expansion in africa}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences}} \textbf{\bibinfo{volume}{95}}, \bibinfo{pages}{8119--8123}
  (\bibinfo{year}{1998}).

\bibitem{meyer2013}
\bibinfo{author}{Meyer, R.~S.} \& \bibinfo{author}{Purugganan, M.~D.}
\newblock \bibinfo{title}{Evolution of crop species: genetics of domestication
  and diversification}.
\newblock \emph{\bibinfo{journal}{Nature Reviews Genetics}}
  \textbf{\bibinfo{volume}{14}}, \bibinfo{pages}{840--852}
  (\bibinfo{year}{2013}).
